MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-17 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
parallel processing with SnowParam
test Total Reads as random effect

library(doParallel)
library(foreach)
library(future)

cl = makeCluster((availableCores()-2)/2)

registerDoParallel(cl)

@@

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
phase3 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("IntragenicRate", "IntronicRate","IntergenicRate","rRNARate", "TotalReads", "GenesDetected", "MappedReads")))
phase3
```

>>>>

library(BiocParallel)
library(foreach)
library(future)

param = SnowParam((availableCores()-2), "SOCK", progressbar=TRUE)
register(param)

@@

#### Phase III (RNASeq alignment specific covariates)
```{r phase3}
phase3 <- mvBIC::mvForwardStepwise(exprObj = subset_CQN,
                         baseFormula = phase2$formula, 
                         data = COVARIATES,
                         variables = array(c("IntragenicRate", "IntronicRate","IntergenicRate","rRNARate", "(1|TotalReads)", "GenesDetected", "MappedReads")))
phase3
```
